Literature Review

### 2020-07-02 Literature_review.tex
Original Literature Review without comments

\item Beyond the methodological breakthrough, our article makes a substantive contribution by documenting many key regularities of party positioning and ideological conflict in the American states. First, despite strong nationalizing trends in American politics, political parties below the national level are quite heterogeneous. Although no Republicans in Congress are more liberal than the most conservative Democrats, we find that many states have Republican state legislative contingents that are more liberal than the Democratic caucuses of many states. Moderate partisans thrive at the state level, just as they languish at the national level. Second, although the low stakes, salience, and information in many state legislative elections would point to a lack of ideological responsiveness, we find that this appears not to be the case. In the aggregate, state legislative medians correlate highly with voter ideology measures. At a more disaggregated level, the ideal points of state legislators correlate highly with presidential vote in their districts. How legislative responsiveness can subsist in such inhospitable environments is a key question for future research.  

@@

@@

\item Evaluating the predictions of a formal model using roll calls faces at least two difficulties. First, the strategic interactions being modeled may be responsible for only a small amount of the variation in the data. Second, the modeling decisions made when analyzing roll calls may make it difficult to correctly characterize the variation of theoretical interest. Unlike the preferences of formal models that are exogenous primitives (McCarty \& Meirowitz 2007), \textbf{the ideal point estimates produced from roll call analyses reflect the preferences members reveal in their behavior as interpreted through the application of a statistical model to an underlying model of individual choice}. Even if the variation predicted by the model is empirically discernible, the predictions of a formal model might still not be supported by roll call estimates if (a) the formal model is wrong, (b) the formal model is correct but a statistical model used to generate or evaluate the estimates is wrong, or (c) both the formal and statistical models are wrong. 

@@

\item The presence of voting error is absolutely critical for roll call analyses because only ordinal rankings are identified with perfect (i.e., errorless) spatial voting (Poole 2000, 2005). If the assumption of probabilistic voting error is violated in some legislatures other methods may be required (e.g., Rosenthal \& Voeten 2004).
\item Even if legislators vote probabilistically, however, \textbf{how the voting errors occur in the model of individual choice may matter}. Standard roll call estimators assume that legislators sometimes vote incorrectly despite perfectly knowing their ideal point and the location of the proposals being voted on. \textbf{The assumed voting error is therefore not attributable to uncertainty about the proposals being voted on or the ideal point that the legislator is attempting to implement.}  Instead, each legislator experiences an independent and identically distributed exogenous shock to her calculation of which alternative is closer to her ideal point on every vote.
\item Alternative specifications of voting error are certainly possible, but the literature has only briefly explored them. Ladha (1991), for example, presents a probabilistic voting model where legislators idiosyncratically and imperfectly perceive the proposal being voted on, and Lauderdale (2010) allows for heteroskedastic voting error.

@@

\item As an illustration, I explore how the selection model and the amount of voting error affect the recovery of true preferences using roll calls. I use a simulation study to demonstrate the importance of the roll call selection model and I characterize how the effect depends on the amount of voting error that is assumed to be present in the data-generating process. To be clear, the investigation is intended only to illustrate how simulations might be used to better understand the properties of roll call estimators when applied to particular contexts. 

@@

\item I found that the heteroskedastic estimator slightly outperforms the homoskedastic estimator at recovering the relative positions of ideal points, even when the true data-generating process is homoskedastic. 

@@

\item The homoskedastic model assumes that all individuals make the same magnitude voting errors, so when, for example, a democrat senator votes differently from ideologically similar senators, they are shifted towards the center, even if the reasons they deviated had nothing to do with the primary axis. The heteroskedastic model yields a more nuanced interpretation of the roll call data. 
\item The heteroskedastic estimator identifies that the individuals deviations are unrelated to the individual's primary axis position, because they do not match the deviations that most moderate indiciduals (from the same ideological party) make.
\item Just as heteroskedasticity can capture motivations that cannot be captured by a small number of spatial dimensions, it can also capture dimensions that were simply omitted. Examining legislators with large “phi(i)” (heteroskedastic parameter) is analogous to examining units with large residuals in a regression model. If many legislators who are difficult to predict have some shared substantive attribute, it is likely that adding another dimension to the model is justified. This diagnostic function of the heteroskedastic model os quite useful when one is interested in a high dimentional legislature like the EU parlament. Hix, Noury and Roland (2006, 2007) have demostrated that the EU Parlament can be effectively modeled using spatial modeling techniques. 

@@

\item “Lobbying, Campaign Contributions and Political Competition” J Rivas - 2017

\item (Question: Is there anything about uncertainty in this paper?)
\item Answer: There is, the second and third bullet point has an overview of the way the paper treats uncertainty.

\begin{itemize}
\item The purpose of this paper is to study how lobbying affects elections where candidates that are running for office can benefit from the funds offered by the lobbies in an exchange for adopting a political position favorable to these lobbies but different from that of the median voter.
\item we show that uncertainty about the voter’s behavior will increase polarization only for the party that gets offered the contract from the higher valuation lobby while it will decrease the polarization of the other party. This is because as uncertainty about the voter goes up adopting a more polarized position becomes less risky. The high valuation lobby takes advantage of this by asking its party for a more polarized position while the low valuation lobby instead allows its party to become less polarized to be in a better position against the now more polarized opposing party.
\item we obtain that uncertainty about the voter also increases the relative spending of the party associated with the high valuation lobby. This is because, as discussed in the previous paragraph, increasing uncertainty increases the polarization of the party associated with the high valuation lobby, which implies that now this lobby has to compensate its party by offering more funds proportional to the funds the other lobby offers.
\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
\item The model described above (previous paragraph in the paper) leads to a two stage four player Bayesian game where in the first stage each lobby simultaneously offers a contract to a different party, then in the second stage parties simultaneously and without knowing the contract offered to the other party decide whether to accept or to reject the contract. In a final stage which party wins the election is declared and its policy position implemented. We solve this game by finding its unique equilibrium and then we proceed to study how the different parameters in the model affect parties’ polarization, campaign spending, and voter’s welfare. 
\item In our results about polarization we find, among others, that the lobby that has a higher stake in the election (the high valuation lobby henceforth) forces its party to adopt a more polarized position than the other party. Although a more polarized position decreases voter support, this can be partly compensated by a higher campaign spending, which the high valuation lobby is willing to fund. 
\item In terms of campaign spending, we find that the higher valuation lobby will contribute more to campaign spending. Furthermore, we also find that the salience of the election decreases total campaign spending but increases the relative campaign spending of the party associated with the high valuation lobby (relative to the other party’s campaign spending). 
\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
\item This is a Bayesian game model, do not use data, only the Bayesian Equilibrium solution concept to characterize the model.

@@

\begin{itemize}
\item We approach the lobbying process as one where cash-for-favour exchanges occur as a means to obtain access to legislators. The model takes into account the \textbf{degree of uncertainty} on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies. Instead, we adopt a simultaneous lobbying structure to capture how lobbying proceeds behind closed doors.
\item In this paper, we find that the degree of uncertainty of legislator preferences, given by the length of the bias intervals, directly affects the bidding strategy of lobbyists. At low levels of uncertainty, lobbyists bid aggressively. The bias of the legislator is not high enough to risk losing the legislator’s support. 
\item We explore \textbf{uncertainty} by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al. (2006).  However, uncertainty is rarely explored on its own. We redirect the focus of the paper to lobbyist interactions over one non-strategic legislator. We remove the dimension of budget allocation and instead assume that the lobbyists are willing to pay at most the value of the legislator support. The results show that uncertainty on its own can provide some good insights on how lobbying unfolds. 
\item We also include a measure of the legislator’s level of integrity. As with Che and Gale (1998), the politician does not hold an open sale for his support given restrictions on vote buying. We can think about this from the perspective of a reputation conscious politician. A reputation conscious politician may not want to be associated with more than one lobbying group for an issue, and would like to be viewed as consistent and honest by her constituents. The more controversial an issue is, the more likely it is for the politician’s threshold to be higher.

@@

\item To facilitate computation, the authors introduce auxiliary random variables.

@@

\item We illustrate the model through an analysis of preferences in different policy domains using recorded votes from the 97th to 114th U.S. House of Representatives (1981 - 2016). Motions brought to a vote in the U.S. Congress differ thematically by substantive issue (e.g., the economy, environment, criminal justice, etc.). We use the Policy Agendas Project main topic coding to categorize roll call votes by issue area (Adler \& Wilkerson, 2017; Policy Agendas Project, 2017). This taxonomy, which consists of 20 mutually exclusive major topics (e.g., Macroeconomics, Health, Environment, etc.), has been used to study legislative agendas (Baumgartner \& Jones, 1993) and attention (Jones \& Baumgartner, 2005), among other matters. 
\item We focus on the PAP categorization for two reasons. First, the application to issue areas illustrates the novel technical contributions of the model, namely (1) comparable revealed preferences across issues and (2) estimates of legislator-specific dimensionality. Second, as argued in Section 3, applying the model to votes grouped by issue area is relevant to the literature on dimensionality (Aldrich et al., 2014; Roberts et al., 2016; Talbert \& Potoski, 2002) by providing issue-specific revealed preference and an estimate of individual consistency – the posterior probably that a member has the same revealed preference in each issue area.

@@

\item Our model not only provides information about the identity of movers, but also about the nature of the issues in which they are movers, and the direction of preference changes. Similar to the procedure we used to define issue-specific ASFs, start by defining a member’s basic ideal point as their ideal point in their base cluster, and say a member has deviant preferences – preferences different than their basic ideal point – on issues not in their base cluster.
\item Figure 7 compares member’s basic ideal point against the ideal points associated with four PAP issues for legislators in the 111th House (Banking and Finance, Civil Rights, Government Operations and Macroeconomics). More specifically, these ternary
plots show the probability that a member’s ideal point in a specific issue is either left of, right of, or the same as their basic ideal point.
\item We compare our illustration to Gerrish and Blei (2012b). While a direct comparison is not possible (as there voters have a main preference and issue-specific deviations), some of the insights provided by both models are similar. Gerrish and Blei (2012b) find votes on appropriations, finance, energy and public lands to have the most movement (issues for which issue-specific preferences deviate the most from members’ base preferences, roughly akin to our deviant issues). Likewise they find issues with the lease amount of movement to be defence and military, education and foreign policy. Looking at the 111th House in particular, they find members preferences on Civil Rights to exhibit very little deviance from their base preference, which is somewhat different from our findings. We both, however, do find a considerable amount of movement/ deviance in the domain of Government Operations.
\item The author claimed that their model is less noicy than previous mocels in the literature, Figure 8. This is because their joint model borrows information across voting domains to estimate the ideal points, leading to lower \textbf{uncertainty}.
\item A key issue to appreciate here (in Figure 8) is that the uncertainty associated with the estimates of ranks varies drastically. Generally speaking, the uncertainty associated with the rank of legislators that are close to the median voter of their own party tends to be much larger than the uncertainty associated with the ranks of centrist or radical legislators (Figure 4). Similarly, the uncertainty in the estimates of the ranks can vary substantially between parties (in the case of the 111th, the uncertainty associated with the
ranks of Democrats is much larger than that of Republicans). As a consequence, changes in ranks for centrist, partisans and Republicans are easier to identify.

@@

\item “Estimating ideal points from roll-call data: explore principal components analysis, especially for more than one dimension?” RF Potthoff - Social Sciences, 2018 
\begin{itemize}
\item The two main existing avenues for estimation of ideal points from roll-call data are the Poole-Rosenthal (P-R) approach and a Bayesian approach (CJR). We examine both of them critically, particularly for more than one dimension, before turning to detailed study of principal components analysis, a technique that has rarely seen use for ideal-point estimation but offers much promise. 
\item The paper works as a comparison between the (P-R), CJR and the PCA (principal components analysis) model, been the latest the one the author is advocating for.  
\item In two or more dimensions (there is no problem in one dimension), the gravest flaw of both P-R and CJR is their nonidentifiability of ideal points—nonidentifiability that goes beyond the simple indefiniteness of location, scale, and orientation. Unlimited numbers of transformations (ones that do not just change location or scale) produce shifts to new sets of ideal points that are substantively different but leave the maximized log likelihood unchanged. Troubles escalate as the number of dimensions increases. 
\item Recognizing the nonidentifiability of CJR in two dimensions, Jackman (2001) sought to circumvent it by assigning certain priors to two roll calls chosen to serve as second- dimension anchors. However, this patch seems arbitrary and subjective. 
\item For two or more dimensions, P-R has far more parameters than CJR (thus entailing worse identifiability troubles) yet even CJR itself lacks identifiability. 
\item As will be seen shortly, PCA does not have any of the characteristics that have just been described. It does not suffer from nonidentifiability, it enjoys the orthogonality property, and its ideal-point estimates for a given dimension do not change when the number of dimensions changes. Several further modeling issues, in the form of arbitrary parameter constraints or identification assumptions, cause trouble for P-R. None of them apply to either CJR or PCA. 
\item The author then explains how to use the PCA model to obtain ideal points with roll call data.  
\item PCA provides no means to assess uncertainty. CJR uses Bayesian methodology to estimate uncertainty for estimates of ideal points and other parameters. Lewis and Poole (2004) proposed parametric-bootstrap standard errors to handle uncertainty assessment for P-R. Both the P-R and CJR techniques, however, rely on an ungrounded assumption of (mutual) conditional independence of a legislator’s votes given the ideal points and roll-call parameters. Although for PCA one may try to find complex standard-error formulas that steer clear of that assumption, it appears that, whether for P-R, CJR, or PCA, any \textbf{effort to assess uncertainty is fraught with impediments}. 
\item Unlike P-R and CJR, PCA does not use a utility function in deriving its model. However, in its theory it is still based on a spatial voting model, just as P-R and CJR are. 
\item (conclusion) for two or more dimensions, whose study may be fruitful for varied situations (e.g., for certain locales and time periods or certain subsets of votes or legislators), the relative benefits of PCA are especially striking and should suffice to make PCA a preeminent contender.

\item "The geometry of multidimensional quadratic utility in models of parliamentary roll call voting" KT Poole - Political Analysis, 2001
\item The purpose of this paper is to show how the geometry of the quadratic utility function in the standard spatial model of choice can be exploited to estimate a model of parliamentary roll call voting.
\item In a standard spatial model of parliamentary roll call voting, the legislator votes for the policy outcome corresponding to Yea if her utility for Yea is greater than her utility for Nay. The voting decision of the legislator is modeled as a function of the difference between these two utilities. The difference between two quadratic utilities has a simple geometric interpretation that can be exploited to estimate legislator ideal points and roll call parameters in a standard framework where the stochastic portion of the utility function is normally distributed.
\item To reiterate, if voting is perfect, that is, sincere and without error, then in one dimension the legislator ideal points and the roll call midpoints are identified only up to a joint rank ordering. In more than one dimension, legislators are identified up to regions in the space (polytopes) and roll calls are identified up to cone-shaped regions containing the normal vectors and line segments on the normal vectors for the midpoints. These limits on identifica tion arise because the data are simply Yea and Nay. If legislators could report "thermometer scores" for the alternatives, then the perfect case would have an exact solution.
\item With quadratic utility, only the location of the cutting hyperplane and the signed distance between the Yea and the Nay alternatives can be estimated. In this framework, there is an infinite number of pairs of Yea and Nay points that produce the same hyperplane and signed distance. 
\item In contrast, an advantage to the normal distribution deterministic utility function used in NOMINATE is that it introduces enough nonlinearities in the utility differences to identify actual positions of the Yea and Nay alternatives. These points have to be used with some caution (Poole and Rosenthal 1997, Appendix A) but it is important to note that the use of the quadratic utility function precludes the estimation of specific Yea and Nay points.
\item Turning to the stochastic portion of the utility function stated in Eq. (3), three probability distributions have been used to model the error: the normal (Ladha 1991; Londregan 2000), uniform (Heckman and Snyder 1997), and logit (Poole and Rosenthal 1997). The normal is clearly the best from both a theoretical and a behavioral standpoint. 
\item From a statistical standpoint, given the difference between the two random errors, the standard assumptions are that they are a random sample (independent and identically distributed random variables) from a known distribution. Hence, it is therefore easy to write down the probability distribution of the difference.
\item  From a behavioral standpoint, it seems sensible to assume that the distributions of the diffrence of the errors are symmetric and unimodal and that they are uncorrelated. The normal distribution is the only one of the three distributions to satisfy all these criteria.
\item A further difficulty with the approaches taken both by Heckman and Snyder and by Poole and Rosenthal is that they assume that the error variance is homoskedastic. A more realistic assumption is that the error variance varies across the roll call votes and across the legislators. For the roll calls, it is impossible to distinguish between the underlying unknown error variance and the distance between the Yea and the Nay alternatives (Ladha 1991; Londregan 2000). The intuition behind this is straightforward. As the distance between the Yea and the Nay alternatives increases, the easier it is for legislators to distinguish between the two policy outcomes and the less likely it is that they make an error. Conversely, if the Yea and Nay alternatives are very close together, then the utility difference is small and it is more likely that voting errors occur. Increasing/decreasing the distance is equivalent to decreasing/increasing the variance of the underlying error
\item The approach developed in Section 5 allows the error to be heteroskedastic. The optimal classification algorithm developed by Poole (2000) can be used to obtain excellent estimates for the legislator points, the jc, 's, the roll call normal vectors, the nj's, and the cutpoints, the m/s.
\item The multidimensional quadratic utility model (QN) can be efficiently estimated in four steps. Within each step the approach taken is to estimate one parameter at a time with all the remaining parameters being held fixed. That is, the maximum of the likelihood function is found for the parameter being estimated conditioned on all the remaining parameters being held fixed. The algorithm always moves uphill in a city block-like fashion. At convergence, every parameter is at a maximum conditioned on all the remaining parameters being held fixed. Convergence to the true global maximum cannot be guaranteed but the conditional global maximum that the algorithm reaches is almost certainly close to the overall global maximum. Although this is not an EM algorithm, it is similar in spirit because the log likelihood always increases from one step to the next.
\item Section 6 compares the Monte Carlo test with other scaling procedures. 
\item Given the computational difficulties in more than one dimension, an attractive alternative to obtain standard errors is a bootstrap analysis. 
\item Because obtaining good-quality standard errors for the parame ters of spatial models of parliamentary voting is very difficult, embedding the geometry in the innovative MCMC work of Jackman (2000) would produce an alternative method of assessing uncertainty in the multidimensional spatial model.
\item The purpose of this paper was to show a method of estimating a multidimensional spatial voting model with quadratic utility and normally distributed errors. The geometry of the multidimensional quadratic utility function can be exploited to estimate legislator ideal points and roll call cutting planes in a standard framework where the stochastic portion of the utility function is normally distributed. The QN scaling procedure is quite stable and does a good job in recovering the true legislator configuration in Monte Carlo tests. 
\item The QN scaling procedure produces legislator configurations that are very similar to those produced by other scaling algorithms. A unique feature of QN is that it allows the variance of the error to vary across legislators. Although the legislator error variances are related to the level of correct classification, more than just correct classification is at work.

>>>>

\item (Conclusion) Beyond the methodological breakthrough, our article makes a substantive contribution by documenting many key regularities of party positioning and ideological conflict in the American states. First, despite strong nationalizing trends in American politics, political parties below the national level are quite heterogeneous. Although no Republicans in Congress are more liberal than the most conservative Democrats, we find that many states have Republican state legislative contingents that are more liberal than the Democratic caucuses of many states. Moderate partisans thrive at the state level, just as they languish at the national level. Second, although the low stakes, salience, and information in many state legislative elections would point to a lack of ideological responsiveness, we find that this appears not to be the case. In the aggregate, state legislative medians correlate highly with voter ideology measures. At a more disaggregated level, the ideal points of state legislators correlate highly with presidential vote in their districts. How legislative responsiveness can subsist in such inhospitable environments is a key question for future research.  

@@

(This paper is very good initial step to understand this topic, very clear explanations of the models, uses and problems)  

@@

\item Evaluating the predictions of a formal model using roll calls faces at least two difficulties. First, the strategic interactions being modeled may be responsible for only a small amount of the variation in the data. Second, the modeling decisions made when analyzing roll calls may make it difficult to correctly characterize the variation of theoretical interest. Unlike the preferences of formal models that are exogenous primitives (McCarty \& Meirowitz 2007), the ideal point estimates produced from roll call analyses reflect the preferences members reveal in their behavior as interpreted through the application of a statistical model to an underlying model of individual choice. Even if the variation predicted by the model is empirically discernible, the predictions of a formal model might still not be supported by roll call estimates if (a) the formal model is wrong, (b) the formal model is correct but a statistical model used to generate or evaluate the estimates is wrong, or (c) both the formal and statistical models are wrong. 

@@

\item Even if legislators vote probabilistically, however, how the voting errors occur in the model of individual choice may matter. Standard roll call estimators assume that legislators sometimes vote incorrectly despite perfectly knowing their ideal point and the location of the proposals being voted on. The assumed voting error is therefore not attributable to uncertainty about the proposals being voted on or the ideal point that the legislator is attempting to implement.  Instead, each legislator experiences an independent and identically distributed exogenous shock to her calculation of which alternative is closer to her ideal point on every vote.

@@

@@

\item For the following Monte Carlo simulations, I begin by generating profiles of data generating parameters. I draw legislator ideal points xh ocj, and Pj from their prior distributions and 1/”phi” from a uniform distribution U(l - d, 1 + S). I simulate data with 3 = 0, 0.25, 0.5. The highest value of S approximates estimates from recent sessions of the U.S. House. I also vary the number of legislators n and the number of roll call votes m across values of 10, 32,100, and 320. For each of the 48 intersections of these parameters, I simulate 50 roll call matrices. I then compute mean posterior estimates for x and o* using both the homoskedastic estimator and the heteroskedastic estimator (both implemented in MCMCpack, Martin and Quinn 2009) on each simulated roll call matrix. 
\item The heteroskedastic estimator slightly outperforms the homoskedastic estimator at recovering the relative positions of ideal points, even when the true data-generating process is homoskedastic. 

@@

\item Just as heteroskedasticity can capture motivations that cannot be captured by a small number of spatial dimensions, it can also capture dimensions that were simply omitted. Examining legislators with large “phi(i)” (heteroskedastic parameter) is analogous to examining units with large residuals in a regression model. If many legislators who are difficult to predict have some shared substantive attribute, it is likely that adding another dimension to the model is justified.

@@

\item “Lobbying, Campaign Contributions and Political Competition” J Rivas - 2017   
\begin{itemize}
\item The purpose of this paper is to study how lobbying affects elections where candidates that are running for office can benefit from the funds offered by the lobbies in an exchange for adopting a political position favorable to these lobbies but different from that of the median voter.
\item The model described above (previous paragraph in the paper) leads to a two stage four player Bayesian game where in the first stage each lobby simultaneously offers a contract to a different party, then in the second stage parties simultaneously and without knowing the contract offered to the other party decide whether to accept or to reject the contract. In a final stage which party wins the election is declared and its policy position implemented. We solve this game by finding its unique equilibrium and then we proceed to study how the different parameters in the model affect parties’ polarization, campaign spending, and voter’s welfare. 
\item In our results about polarization we find, among others, that the lobby that has a higher stake in the election (the high valuation lobby henceforth) forces its party to adopt a more polarized position than the other party. Although a more polarized position decreases voter support, this can be partly compensated by a higher campaign spending, which the high valuation lobby is willing to fund. 
\item In terms of campaign spending, we find that the higher valuation lobby will contribute more to campaign spending. Furthermore, we also find that the salience of the election decreases total campaign spending but increases the relative campaign spending of the party associated with the high valuation lobby (relative to the other party’s campaign spending). 
\item From the point of view of welfare measured as the utility of the median voter, we find among others that competition between lobbies, i.e. when both have similar valuations, minimizes welfare. 
\item This is a Bayesian game model, do not use data, only the Bayesian Equilibrium solution concept to characterize the model.

@@

\begin{itemize}
\item We approach the lobbying process as one where cash-for-favour exchanges occur as a means to obtain access to legislators. The model takes into account the degree of uncertainty on a non-strategic legislator’s preference, the legislator’s level of integrity, and the perceived advantages each lobbyist may have on their respective policies. Instead, we adopt a simultaneous lobbying structure to capture how lobbying proceeds behind closed doors.
\item In this paper, we find that the degree of uncertainty of legislator preferences, given by the length of the bias intervals, directly affects the bidding strategy of lobbyists. At low levels of uncertainty, lobbyists bid aggressively. The bias of the legislator is not high enough to risk losing the legislator’s support. 
\item We explore uncertainty by focusing on lobbyist behavior when faced with uncertain legislator preferences similar to Buzard and Saiegh (2016) and Dekel et al. (2006).  However, uncertainty is rarely explored on its own. We redirect the focus of the paper to lobbyist interactions over one non-strategic legislator. We remove the dimension of budget allocation and instead assume that the lobbyists are willing to pay at most the value of the legislator support. The results show that uncertainty on its own can provide some good insights on how lobbying unfolds. 
\item We also include a measure of the legislator’s level of integrity. As with Che and Gale (1998), the politician does not hold an open sale for his support given restrictions on vote buying. We can think about this from the perspective of a reputation conscious politician. A reputation conscious politician may not want to be associated with more than one lobbying group for an issue, and would like to be viewed as consistent and honest by her constituents. The more controversial an issue is, the more likely it is for the politician’s threshold to be higher.

@@

@@

@@

@@

\item “Estimating ideal points from roll-call data: explore principal components analysis, especially for more than one dimension?” RF Potthoff - Social Sciences, 2018 
\begin{itemize}
\item The two main existing avenues for estimation of ideal points from roll-call data are the Poole-Rosenthal (P-R) approach and a Bayesian approach (CJR). We examine both of them critically, particularly for more than one dimension, before turning to detailed study of principal components analysis, a technique that has rarely seen use for ideal-point estimation but offers much promise. 
\item The paper works as a comparison between the (P-R), CJR and the PCA (principal components analysis) model, been the latest the one the author is advocating for.  
\item In two or more dimensions (there is no problem in one dimension), the gravest flaw of both P-R and CJR is their nonidentifiability of ideal points—nonidentifiability that goes beyond the simple indefiniteness of location, scale, and orientation. Unlimited numbers of transformations (ones that do not just change location or scale) produce shifts to new sets of ideal points that are substantively different but leave the maximized log likelihood unchanged. Troubles escalate as the number of dimensions increases. 
\item Recognizing the nonidentifiability of CJR in two dimensions, Jackman (2001) sought to circumvent it by assigning certain priors to two roll calls chosen to serve as second- dimension anchors. However, this patch seems arbitrary and subjective. 
\item For two or more dimensions, P-R has far more parameters than CJR (thus entailing worse identifiability troubles) yet even CJR itself lacks identifiability. 
\item As will be seen shortly, PCA does not have any of the characteristics that have just been described. It does not suffer from nonidentifiability, it enjoys the orthogonality property, and its ideal-point estimates for a given dimension do not change when the number of dimensions changes. Several further modeling issues, in the form of arbitrary parameter constraints or identification assumptions, cause trouble for P-R. None of them apply to either CJR or PCA. 
\item The author then explains how to use the PCA model to obtain ideal points with roll call data.  
\item PCA provides no means to assess uncertainty. CJR uses Bayesian methodology to estimate uncertainty for estimates of ideal points and other parameters. Lewis and Poole (2004) proposed parametric-bootstrap standard errors to handle uncertainty assessment for P-R. Both the P-R and CJR techniques, however, rely on an ungrounded assumption of (mutual) conditional independence of a legislator’s votes given the ideal points and roll-call parameters. Although for PCA one may try to find complex standard-error formulas that steer clear of that assumption, it appears that, whether for P-R, CJR, or PCA, any effort to assess uncertainty is fraught with impediments. 
\item Unlike P-R and CJR, PCA does not use a utility function in deriving its model. However, in its theory it is still based on a spatial voting model, just as P-R and CJR are. 
\item (conclusion) for two or more dimensions, whose study may be fruitful for varied situations (e.g., for certain locales and time periods or certain subsets of votes or legislators), the relative benefits of PCA are especially striking and should suffice to make PCA a preeminent contender. 
\end{itemize}
